\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-10 journalSwarmControl/experiment.tex
fixed terminology

Unfortunately, when the swarm is in front of the object, control law \eqref{eq:PDcontrolPosition} pushes the object backwards.  To fix this, we implement a potential field approach \cite{spong2008robot} that attracts the swarm to the intermediate goal, but repulses the swarm from in front of the object.
The repulsive potential field is centered at the object's COM and is active for a radius $\rho_0$, but is implemented only when the swarm mean is within $\theta$ of the desired direction of motion $\mathbf{D}$ as shown in Fig.~\ref{fig:potentialField}.
\begin{align}
F_{att} &= -\zeta \Delta \rho / \rho \\
%\mathbf{u} &= [\bar{x},\bar{y}] - \mathbf{b} \nonumber \\
\phi &=\cos^{-1}\left( \frac{ \mathbf{D} \cdot ( [\bar{x},\bar{y}] - \mathbf{b}) }{\norm{\mathbf{D}} \norm{ [\bar{x},\bar{y}] - \mathbf{b}} } \right) \\
%\theta &= \mathrm{angularDistance}\left( \alpha, \beta \right)\nonumber \\
 F_{rep} &=  \left\{
\begin{array}{ll}
      \eta( 1/\rho- 1/\rho_0) \frac{1}{\rho^2} \Delta \rho, ~& \rho\leq \rho_0~\&~\phi <  \theta \\
      0, & \textrm{ otherwise} \\
\end{array} 
\right.\\
F_{pot} &= F_{att} + F_{rep} \label{eq:potentialfield}
\end{align}

>>>>

Unfortunately, when the swarm is in front of the object, control law \eqref{eq:PDcontrolPosition} pushes the object backwards.  To fix this, we implement a potential field approach \cite{spong2008robot} that attracts the swarm to the intermediate goal, but repulses the swarm from in front of the object.
The repulsive potential field is centered at the object's COM and is active for a radius $\rho_0$, but is implemented only when the swarm mean is within $\theta$ of the desired direction of motion $\mathbf{D}(\mathbf{b})$ as shown in Fig.~\ref{fig:potentialField}.
\begin{align}
F_{att} &= -\zeta \Delta \rho / \rho \\
%\mathbf{u} &= [\bar{x},\bar{y}] - \mathbf{b} \nonumber \\
\phi &=\cos^{-1}\left( \frac{ \mathbf{D}(\mathbf{b}) \cdot ( [\bar{x},\bar{y}] - \mathbf{b}) }{\norm{\mathbf{D}(\mathbf{b})} \norm{ [\bar{x},\bar{y}] - \mathbf{b}} } \right) \\
%\theta &= \mathrm{angularDistance}\left( \alpha, \beta \right)\nonumber \\
 F_{rep} &=  \left\{
\begin{array}{ll}
      \eta( 1/\rho- 1/\rho_0) \frac{1}{\rho^2} \Delta \rho, ~& \rho\leq \rho_0~\&~\phi <  \theta \\
      0, & \textrm{ otherwise} \\
\end{array} 
\right.\\
F_{pot} &= F_{att} + F_{rep} \label{eq:potentialfield}
\end{align}
